---
title: "Original Recycling Model Replication Analysis"
author: "Emily Coco"
date: "1/19/2021"
output: html_document
---

```{r setup, echo=F, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(stringr)
theme_set(theme_bw())
```

## Introduction

*note changes to model here

```{r cars, echo = F}
setwd("/Users/emilycoco/eclipse-workspace/recycling-Java/analysis")
load("site-types.RData")
st = site.types

#calculation of important variables
st$length = nchar(st$sitecode)
st$A = str_detect(st$sitecode, pattern = "1")
st$B = str_detect(st$sitecode, pattern = "2")
st$AB = str_detect(st$sitecode, pattern = "3")
st$M1 = str_detect(st$sitecode, pattern = "4")
st$M2 = str_detect(st$sitecode, pattern = "5")
st$fulltrans = str_detect(st$sitecode, pattern = "2+4+1+")
st$trans.UP = str_detect(st$sitecode, pattern = "2+4+")
st$MP.trans = str_detect(st$sitecode, pattern = "4+1+")
st$notrans = !st$M1 & !st$M2
st$allmix = !str_detect(st$sitecode, pattern = "1") &
  !str_detect(st$sitecode, pattern = "2") & 
  !str_detect(st$sitecode, pattern = "3")
st$trans.MP = str_detect(st$sitecode, pattern = "1+4+") |
  str_detect(st$sitecode, pattern = "1+5+") #this is important
st$UP.trans = str_detect(st$sitecode, pattern = "4+2+") |
  str_detect(st$sitecode, pattern = "5+2+")
st$back.trans = str_detect(st$sitecode, pattern = "1+4+2+")

randomED = st %>% filter(ed == 0.5)
EDdif = st %>% filter(ed == 0.25 | ed == 0.75)

props = randomED %>% group_by(overlap, total.groups, ed.freq) %>%
  summarize(A = sum(A, na.rm = TRUE)/n(),
            B = sum(B, na.rm = TRUE)/n(),
            AB = sum(AB, na.rm = TRUE)/n(),
            M1 = sum(M1, na.rm = TRUE)/n(), 
            M2 = sum(M2, na.rm = TRUE)/n(), 
            ft = sum(fulltrans, na.rm = TRUE)/n(), 
            tU = sum(trans.UP, na.rm = TRUE)/n(), 
            Mt = sum(MP.trans, na.rm = TRUE)/n(), 
            nt = sum(notrans, na.rm = TRUE)/n(), 
            allmix = sum(allmix, na.rm = TRUE)/n(), 
            tM = sum(trans.MP, na.rm = TRUE)/n(), 
            Ut = sum(UP.trans, na.rm = TRUE)/n(), 
            bt = sum(back.trans, na.rm = TRUE)/n())

props$overlap = factor(props$overlap, levels = c("1", "0.5", "0"))
props$total.groups = factor(props$total.groups, levels = c("10", "18", "36"))
props$ed.freq = factor(props$ed.freq, levels = c("2", "10", "20"))

st2 = site.types
st2$A = str_count(st2$sitecode, pattern = "1")
st2$B = str_count(st2$sitecode, pattern = "2")
st2$AB = str_count(st2$sitecode, pattern = "3")
st2$M1 = str_count(st2$sitecode, pattern = "4")
st2$M2 = str_count(st2$sitecode, pattern = "5")

randomED2 = st2 %>% filter(ed == 0.5)
EDdif2 = st2 %>% filter(ed == 0.25 | ed == 0.75)

counts = randomED2 %>% group_by(overlap, total.groups, ed.freq) %>%
  summarize(A = sum(A, na.rm = TRUE),
            B = sum(B, na.rm = TRUE),
            AB = sum(AB, na.rm = TRUE),
            M1 = sum(M1, na.rm = TRUE), 
            M2 = sum(M2, na.rm = TRUE))

counts$overlap = factor(counts$overlap, levels = c("1", "0.5", "0"))
counts$total.groups = factor(counts$total.groups, levels = c("10", "18", "36"))
counts$ed.freq = factor(counts$ed.freq, levels = c("2", "10", "20"))


```

## Relational Alignment Analysis

Proportions of sites with particular types of assemblages by parameters:

```{r counts} 
##not exactly like Fig 2 in the paper -- will need to count assemblages for that
atypes = counts %>% select(overlap, total.groups, ed.freq, A, B, AB, M1, M2) %>% 
  pivot_longer(c(A, B, AB, M1, M2), names_to = "type", values_to = "proportion") %>% filter(proportion != 0)

atypes$type = factor(atypes$type, levels = c("M2", "M1", "AB", "B", "A"))

ggplot(atypes, aes(x = as.factor(ed.freq), y = as.factor(type), color = as.factor(type))) +
  geom_point(aes(size = proportion)) +
  facet_grid(total.groups ~ overlap, labeller = label_both) +
  scale_color_colorblind() +
  guides(color = "none", size = "none")
```


Proportions of sites with at least one M1 assemblage by parameters:

```{r M1-assemblages}
#summary(counts$M1)

ggplot(data = props, aes(x = as.factor(ed.freq), y = as.numeric(M1), group = as.factor(ed.freq))) +
  geom_boxplot() +
  facet_grid(total.groups ~ overlap, labeller = label_both)
  

```


Proportions of sites with at least one M2 assemblage by parameters:

```{r M2-assemblages}
#summary(counts$M1)

ggplot(data = props, aes(x = as.factor(ed.freq), y = as.numeric(M2), group = as.factor(ed.freq))) +
  geom_boxplot() +
  facet_grid(total.groups ~ overlap, labeller = label_both)
  

```


Proportions of sites with at least one type of transitional assemblage by parameters:

```{r forward-transitions}
ttypes = props %>% select(overlap, total.groups, ed.freq, ft, tU, Mt) %>% 
  pivot_longer(c(ft, tU, Mt), names_to = "type", values_to = "proportion")
ttypes$type = factor(ttypes$type, levels = c("Mt", "ft", "tU"))

ggplot(ttypes, aes(x = as.factor(ed.freq), y = as.numeric(proportion), color = type)) +
  geom_boxplot() +
  facet_grid(total.groups ~ overlap, labeller = label_both) +
  scale_color_colorblind()
  

```


Proportions of sites with at least one type of reverse transitional assemblage by parameters:

```{r reverse-transitions}
btypes = props %>% select(overlap, total.groups, ed.freq, Ut, tM) %>% 
  pivot_longer(c(Ut, tM), names_to = "type", values_to = "proportion")
btypes$type = factor(btypes$type, levels = c("Ut", "tM"))

ggplot(btypes, aes(x = as.factor(ed.freq), y = as.numeric(proportion), color = type)) +
  geom_boxplot() +
  facet_grid(total.groups ~ overlap, labeller = label_both) +
  scale_color_colorblind()
  

```


Patterns are the same!